\documentclass[12pt,letterpaper]{article}
\usepackage{fullpage}
\usepackage[top=2cm, bottom=4.5cm, left=2.5cm, right=2.5cm]{geometry}
\usepackage{amsmath,amsthm,amsfonts,amssymb,amscd}
\usepackage{lastpage}
\usepackage{enumerate}
\usepackage{fancyhdr}
\usepackage{mathrsfs}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{hyperref}
\usepackage{multicol}

\usepackage{enumitem}


\hypersetup{%
  colorlinks=true,
  linkcolor=blue,
  urlcolor=cyan,
  linkbordercolor={0 0 1}
}
 
\renewcommand\lstlistingname{Algorithm}
\renewcommand\lstlistlistingname{Algorithms}
\def\lstlistingautorefname{Alg.}

\lstdefinestyle{Python}{
    language        = Python,
    frame           = lines, 
    basicstyle      = \footnotesize,
    keywordstyle    = \color{blue},
    stringstyle     = \color{green},
    commentstyle    = \color{red}\ttfamily
}

\setlength{\parindent}{0.0in}
\setlength{\parskip}{0.05in}

% Edit these as appropriate
\newcommand\course{PHYS 243}
\newcommand\hwnumber{3}                  % <-- homework number
\newcommand\MyName{TA: Abtin Shahidi}           % <-- My name

\pagestyle{fancyplain}
\headheight 35pt
\lhead{\MyName}

\chead{\textbf{\Large Mid-term}}
\rhead{\course \\ Deadline:  July 28, 2019, 11:59 pm}
\lfoot{}
\cfoot{}
\rfoot{\small\thepage}
\headsep 1.5em

\begin{document}
\section*{Data sets:}
You can choose any of the following data-sets:

\begin{enumerate}
\item Climate Model Simulation Crashes Data Set 

\item Acute Inflammations Data Set 

\item Teaching Assistant Evaluation Data Set 


\item Wine Quality Data Set 
\end{enumerate}

You can find the information on each data set zip file which contains the data itself, what each columns represents and additional information on the data sets.

\section*{Expectation}
\begin{enumerate}
\item Understanding and explaining the data set, what are the different attributes of each data point.

\item Processing, and cleaning up the data. 

\item Dividing your data into a training and test set. 

\item Choosing the relevant algorithm and why you think it is better fit for this data set.

\item Writing a python code to perform learning. (You can reuse every code from the lectures)

\item Evaluating your learning performance. 

\item Making sure your results does not depend on your choosing parameters.
\end{enumerate}



\end{document}


